### 2012-10-27 paper_draft.tex

In the same timeframe as above, all users combined have 
entered a total of 675 variations on 47 different phenotypes with those variations being 
the different values on a given trait or phenotype. See figure \ref{Figure1_label} for the increase of phenotypic information over time.

The mean number of users that have entered their variations for a single phenotype 
is 14.36 (SD 12.65), the median is 10. The distribution of how many users have 
entered their data per phenotype can be seen in figure \ref{Figure2_label}. The phenotype provided 
by the most users is the eye color, which has been entered by 54 users. There are 
two phenotypes which have so far only been provided by a single user: 
the SAT Writing score and triglyceride-levels.\bastian{update all numbers and graphs}

@@

>>>>

In the same timeframe as above, all users combined have 
entered a total of 4743 variations on 130 different phenotypes with those variations being 
the different values on a given trait or phenotype. The mean number of users that have entered their variations for a single phenotype 
is 36.48. The distribution of how many users have 
entered their data per phenotype , compared to the amount of unique phenotypes, can be seen in figure \ref{pheno}. The phenotype provided by the most users is "eye color", for which 207 users entered their phenotype.

@@

Users are also able to link their Fitbit-accounts to their user-accounts. Fitbit is a commercial service which lets their customers track their BMI, movement-data and sleep data. This data can be linked to openSNP to give interested researchers an automatically maintained dataset of body- and sleep-developments over time.
